%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style


\usepackage[left=0.5in,top=0.6in,right=0.55in,bottom=0.6in]{geometry} % Document margins
\name{Migun Shakya, PhD} % Your name
\address{2020A 23rd st. \\ Los Alamos, NM 87544} % Your address
\address{(505)~$\cdot$~667~$\cdot$~5571 \\ migun.shakya@gmail.com} % Your phone number and email
\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}
{\bf Ph.D} Genome Sciences {$\diamond$} University of Tenneessee {$\diamond$} Knoxville, TN \hfill {2013} \\
\textit{Dissertation:} Validating approaches for studying microbial diversity to \\
characterize communities from roots of \textit{Populus deltoides}


%\item \textit{Dissertation:}Validating approaches for studying microbial diversity to characterize communities from roots of \textit{Populus deltoides}\\
{\bf B.S}  Biology {$\diamond$} Southwerstern Oklahoma State University {$\diamond$}  Weatherford, OK \hfill{2008}
\end{rSection}

%----------------------------------------------------------------------------------------
%	RESEARCH EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Research Experience}
\begin{rSubsection}{Post-doc} {2016 - present}{}{}
\item Bioscience Division, Los Alamos National Laboratory, Los Alamos, NM
\item Developing RNA-seq analysis pipeline to detect differentially expressed genes \\
in eukaryotes and prokaryotes.
\item Developing pipelines to conduct evolutionary analyses directly from raw sequences.
\end{rSubsection}

%------------------------------------------------
\begin{rSubsection}{Post-doc} {2013 - 2016}{}{}
\item Department of Biology, Dartmouth College, Hanover, NH
\item Describe evolution of Gene Transfer Agents (GTAs) across \textit{Alphaproteobacteria}.
\item Developed SVM-based algorithm to distinguish phage genes from their GTA homologs.
\end{rSubsection}

%------------------------------------------------
\begin{rSubsection}{Graduate Research Assistant} {2009 - 2013}{}{}
\item University of Tennessee and Oak Ridge National Lab, Oak Ridge, TN 
\item Analysis of microbiomes from roots of \textit{P. deltoides}.
\item Tested the accuracy of describing microbiome using amplicons.
\end{rSubsection}
\end{rSection}

%------------------------------------------------

\begin{rSection}{Publications}

\item \textbf{Shakya M.}, Soucy S.M., Zhaxybayeva O. (2017). Insights into Origin and Evolution of $\alpha$ -proteobacterial Gene Transfer Agents. \textit{Submitted to Viral Evolution}
\item Hynes A.P*, \textbf{Shakya M.}*, Mercer R.G, Grull M.P, Brown L., Davidson F, Steffen E., Matchem H., Peach M.E, Berger T, Grebe K., Zhaxybayeva O., Lang A.S (2016). Functional and evolutionary characterization of a gene transfer agent's multi-locus ``genome''?, \textit{Molecular Biology and Evolution} *{\tiny These authors contributed equally}
\item D’Amore R., Ijaz, U. Z., Schirmer M., Kenny J. G., Gregory R., Darby A. C., \textbf{Shakya M.}, Podar M., Quince C. and Hall N. (2016). A comprehensive benchmarking study of protocols and sequencing platforms for 16S rRNA community profiling.\textit{BMC genomics} \doi{10.1186/s12864-015-2194-9}
\item Hurt, R.A., Robeson II M.S., \textbf{Shakya M.}, Moberly, J.G., Vishnivetskaya, T.A., Gu B., and Elias, D.A. (2014). Improved Yield of High Molecular Weight DNA Coincides with Increased Microbial Diversity Access from Iron Oxide Cemented Sub-Surface Clay Environments. \textit{Plos ONE}. \doi{10.1371/journal.pone.0102826}
 \item \textbf{Shakya, M.}, Gottel N., Castro H., Yang Z.K., Gunter L., Labbe J., Muchero W., Bonito G., Vilgalys R., Tuskan G., Podar M., Schadt C.W. (2013). A Multifactor Analysis of Fungal and Bacterial Community Structure in the Root Microbiome of Mature Populus deltoides Trees. \textit{Plos ONE}. \doi{10.1371/journal.pone.0076382}
\item \textbf{Shakya, M.}, Quince, C., Campbell, J., Yang, Z., Schadt, C.W., Podar, M (2013). Comparative metagenomic and rRNA microbial diversity characterization using Archaea and Bacteria synthetic communities \textit{Environmental Microbiology}.\doi{10.1111/1462-2920.12086}
\item Flores E.G.,\textbf{Shakya, M.}, Meneghin J.,Podar, M., Seewald., J.S., Reysenbach A-L (2012). Inter-field Variability in the Microbial Communities of Hydrothermal Vent Deposits from a Back-Arc Basin.\textit{Geobiology}. \doi{10.1111/ j.1472-4669.2012.00325.x}
\end{rSection}

%------------------------------------------------
%Book Chapter
%------------------------------------------------
\begin{rSection}{Book Chapters}
\item Culley A.I., \textbf{Shakya M.}, Lang A.S. (2015) Viral evolution at the limits. In \textit{Microbial Evolution under Extreme Conditions} (pp.209-222).Germany.degruyter.
\end{rSection}


%------------------------------------------------
%Scientific Meeting
%------------------------------------------------

\begin{rSection}{Selected Scientific Conferences}

\item \textbf{Shakya M.}. Lets make a tree! PhaME: A tool for Phylogenetic and Molecular Evolution Analysis. In:\emph{LANL B Division Day}, September 14, 2017. Talk.

\item \textbf{Shakya M.}, Senin P., Feng S., Lo C., Hu. B, Chain P.S.G. PiReT: Pipeline for Reference Based Transcriptomics. In:\emph{LANL Postdoc Research Symposium and Career Fair}, August 29-31, 2017.  Poster.

\item Li P.E., Lo C-C., Anderson J., Davenport K., Bishop-Lilly K., Xu Y., Voegtly L., Feng S., Senin P., \textbf{Shakya M.}, Philipson C., Gans J., Miller N., Challacombe J., Hamilton T., Chain P.S.G. Addressing the Analysis Bottleneck Created by Next Generation Sequencing (NGS) Using EDGE Bioinformatics. In:\emph{asm microbe}, June 1-5, 2017. Poster and Selected talk.

\item \textbf{Shakya M.}, Senin P., Feng S., Lo C., Hu. B, Chain P.S.G. PiReT: Pipeline for Reference Based Transcriptomics. In:\emph{Sequencing, Finishing, analysis In the Future Meeting}, May 16-18, 2017. Poster.

\item \textbf{Shakya M.} and Zhaxybayeva O. Do bacteria domesticate viruses?. In:\emph{Microbiology and Molecular Pathogenesis Program Retreat}, February 11-12, 2016. Poster and Talk.

\item \textbf{Shakya M.} and Zhaxybayeva O. Origin and Evolution of gene transfer agents in $\alpha$-proteobacteria. In:\emph{Mobile Genetic Elements: In Silico, In Vitro, In Vivo}, September 3-5, 2015. Selected talk.

\item \textbf{Shakya M.} and Zhaxybayeva O. Origin and Evolution of gene transfer agents in $\alpha$-proteobacteria. In:\emph{Gordon Research Conference: Microbial Population Biology}, July 19-24, 2015. Poster.

\item \textbf{Shakya M.}, Drivers of microbial community structure in rhizosphere and endosphere of \textit{Populus deltoides}.In: \emph{American Society for Microbiology KY-TN Branch Meeting }, October 26-27, 2012.Talk.

\item  \textbf{Shakya M.}, Gottel,N.R., Castro,H.F.,Yang Z.K.,Kerley M., Podar M.,Doktcyz, M.J., Schadt, C.W. Archaea associated with Populus and its surrounding soil and trees.In: \emph{International Society of Microbial Ecology 14, Copenhagen, Denmark}, August 19-24, 2012.Poster.

\item \textbf{Shakya M.}, Gottel,N.R., Castro,H.F.,Yang Z.,Kerley M., Podar M.,Doktcyz, M.J.,Schadt, C.W. Plant-Microbe Interface: Dynamics of Bacterial Microbiome of \textit{Populus deltoides}  In: \emph{2012 Department of Energy Genomic Science Awardee Meeting X}, February 26-29, 2012.Poster.

\item \textbf{Shakya M.}, Campbell, J.C., Schadt, C.W.,Podar M. Experimental and Computational Approaches for Microbial Diversity Characterization Using Artificial Communities.In: \emph{2011 Genomic Science Awardee Meeting IX }, April 10-13 , 2011.Poster and Talk.

\item \textbf{Shakya M.}, Campbell, J.C.,Yang,Z.K., Podar M. Experimental and Computational Approaches for Microbial Diversity Characterization Using Artificial Communities In: \emph{International Society of Microbial Ecology 13}, August 22-27, 2010.Poster.

\end{rSection}
\newpage
%------------------------------------------------
%Teaching experience
%------------------------------------------------

\begin{rSection}{Teaching Experiences}{}{}{}
\href{http://www.lanl.gov}{\bf Los Alamos National Laboratory, Los Alamos, NM }
\item Taught a class on phylogenetic analysis for annual workshop (2017).
\item Taught a class on Transcriptomics analysis for annual workshop (2017).

\href{http://www.utk.edu}{\bf University of Tennessee, Knoxville}
\item Teaching Assistant for BCMB 230 : Human Physiology Fall~2009 (2 sections)
\item Teaching Assistant for BIO 140 : Organization and Function of the Cell  Spring~2010 (2 sections)

\href{http://www.swosu.edu}{\textbf{Southwestern Oklahoma State University}}
 \item Teaching Assistant for Biological Sciences Fall~2007-Spring~2008
\item Grader for College Algebra and Trigonometry Spring~2007-Spring~2008

\end{rSection}

%------------------------------------------------
%Honors and awards
%------------------------------------------------

\begin{rSection}{Honors and Awards}
\href{http://www.utk.edu}{\textbf{University of Tennessee, Knoxville}}
\item 2011 Genomic Sciences Meeting Student Travel Grant

\item \href{http://www.swosu.edu}{\textbf{Southwestern Oklahoma State University}},
\item In-State Tuition Waiver 2003-2008
\item Ottis and Buena Ballard Memorial Scholarship 2007
\item Who is Who Among American Universities 2008
\end{rSection}

%----------------------------------------------------------------------------------------
%	Peer review
%----------------------------------------------------------------------------------------

\begin{rSection}{Peer review activities}
Reviewer for: FEMS Microbiology Ecology, Canadian Journal of Microbiology, Frontiers in Microbiology, Molecular Biology and Evolution, BMC Microbiology, MDPI - \textit{Toxins}
\end{rSection}

%----------------------------------------------------------------------------------------
%   MENTORSHIP
%----------------------------------------------------------------------------------------


\begin{rSection}{Mentorship Experience}
Irene Feng, Dartmouth College (2013-2015).
Dan Birnbaum, Dartmouth College (2015).
Taylor Neely, Dartmouth College (2015-2016).
Camille Hankel, Georgetown College (2016).
\end{rSection}


%----------------------------------------------------------------------------------------
%	BIOINFORMATIC SKILLS
%----------------------------------------------------------------------------------------


\begin{rSection}{Relevant skills}
{\bf Programming/Scripting}: Python, Perl, R, Bioconductor\\
{\bf Bioinformatics}: Analysis of Microbiome, Genome, Microbial ecology, Metagenome, Metagenetics, Methylome, RNA-seq, phylogenetics, etc.\\
{\bf Other}: Linux, shell scripting, high performance computing\\
\end{rSection}


%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------


%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
